Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-05-17 doc/PRF2022/PRF_main.tex
to do list

\item $N_b=60$ structures in a shear flow: For both boundary conditions, lamellar (FIG. 4) and polar (FIG. 4), check convergence using $N=16$ and $N=24$. 
Compare the new results with the current FIG 4. (d). Revise FIG. 5 with more details.

@@

Channel Flow: 
\begin{enumerate}
\item $Nb_25$ vesicle in a narrow channel.
\item $Nb_40$ multi-lamellar structure in a narrow channel.
\end{enumerate}

>>>>

\item $N_b=60$ structures in a shear flow: For both boundary conditions, lamellar (FIG. 4) and polar (FIG. 4), convergence tests using $N=16$ and $N=24$ are not yet verified. 
Compare results using $N_b=24$ with the current FIG 4. (d). Revise FIG. 5 with more details.

@@

Channel Flow: 
\begin{enumerate}
\item Convergence tests for $N_b=25$ vesicle in a narrow channel.  Add energy profile.

\item Convergence tests for $N_b=40$ multi-lamellar structure in a narrow channel. Add energy profile.

\end{enumerate}
